---
title: "Projet M2 2022-23"
subtitle: 'Modèles pour la régression'
author: "Mettre vos noms ICI"
output: 
  pdf_document: 
    keep_tex: no
fontsize: 12pt    
header-includes:
- \usepackage{pifont}
- \usepackage{manfnt}
- \usepackage{mdframed}
- \usepackage{systeme}
- \usepackage{txfonts}
- \newcommand{\cH}{\mathcal{H}}

params:
  path_data_folder: "../data/"
  path_R_folder: "../R/"
---

# Paremeters
```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = 'center', warning=FALSE,message=FALSE)

source(paste(params$path_R_folder,"libraries.R", sep=''))
source(paste(params$path_R_folder,"functions.R", sep=''))
source(paste(params$path_R_folder,"preprocessing.R", sep=''))
set.seed(2022)

init_train <- read.csv2(paste(params$path_data_folder, "train.csv",sep=''),
                   header=TRUE, 
                   sep=",")
init_test <- read.csv2(paste(params$path_data_folder, "test.csv", sep=''), 
                  header=TRUE, 
                  sep=",")

target <- 'SalePrice'
train <- set_numerics(init_train, num_vars)
```

# EDA
```{r}
train %>% head()
train %>% str()
train %>% summary()
```

### Correlation
```{r}
get_correlation(train)
```

# EDA by var

### SalePrice
```{r}
var <- 'SalePrice'

train[,var] %>% str
train[,var] %>% summary

hist_and_density(train, var, binwidth=10000)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot() +
  labs(x=var)

if(!require(tseries)){install.packages('tseries')}
jarque.bera.test(train[,var])

shapiro.test(train[,var])
```

### YearBuilt
```{r}
var <- 'YearBuilt'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

train[,var] <- train[,var] %>% as.character
boxplot_mano(train, target, var)
train[,var] <- train[,var] %>% as.numeric

ridgeline(train[,target], train[,var])
```


### YrSold
```{r}
var <- 'YrSold'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

train[,var] <- train[,var] %>% as.character
boxplot_mano(train, target, var)
train[,var] <- train[,var] %>% as.numeric

ridgeline(train[,target], train[,var])
```


### MonthSold
dropped cause weak correlation to target

```{r}
var <- 'MonthSold'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

train[,var] <- train[,var] %>% as.character
boxplot_mano(train, target, var)
train[,var] <- train[,var] %>% as.numeric

ridgeline(train[,target], train[,var])
```


### Size.sqf.
```{r}
var <- 'Size.sqf.'

train[,var] %>% str
train[,var] %>% summary

hist_and_density(train, var, binwidth=100)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot()

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm')
```

### Floor
keep it num

```{r}
var <- 'Floor'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

train[,var] <- train[,var] %>% as.factor
boxplot_mano(train, target, var)
train[,var] <- train[,var] %>% as.numeric

ridgeline(train[,target], train[,var])
```

### HallwayType
Niquel don't modify

```{r}
var <- 'HallwayType'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
cor_qual(train, target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])
```

### HeatingType
Not relevant, should be merged, drop

```{r}
var <- 'HeatingType'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
cor_qual(train, target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])
```

### AptManageType
Niquel don't modify

```{r}
var <- 'AptManageType'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
cor_qual(train, target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])
```

### N_Parkinglot.Ground.
Go numeric, se fera probablement tej anyway, cor 20%

```{r}
var <- 'N_Parkinglot.Ground.'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

train[,var] <- train[,var] %>% as.character
boxplot_mano(train, target, var)
train[,var] <- train[,var] %>% as.numeric

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=20)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot()

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm')
```

### N_Parkinglot.Basement.
Numérique? corr 43%

```{r}
var <- 'N_Parkinglot.Basement.'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

train[,var] <- train[,var] %>% as.character
boxplot_mano(train, target, var)
train[,var] <- train[,var] %>% as.numeric

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=20)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot()

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm')
```

### TimeToBusStop
Faible corrélation, do not touch and it will go away

```{r}
var <- 'TimeToBusStop'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
cor_qual(train, target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])

```

### TimeToSubway
0-5 d'un côté (proche), autre durée d'un autre (moins proche x loin)

```{r}
var <- 'TimeToSubway'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
cor_qual(train, target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])
```

### N_APT
cor 5%. on ne touche pas ça partira tout seul.

```{r}
var <- 'N_APT'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

train[,var] <- train[,var] %>% as.character
boxplot_mano(train, target, var)
train[,var] <- train[,var] %>% as.numeric

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=1)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot()

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm')
```

### N_manager
```{r}
var <- 'N_manager'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

train[,var] <- train[,var] %>% as.character
boxplot_mano(train, target, var)
train[,var] <- train[,var] %>% as.numeric

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=1)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot()

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm')
```


### N_elevators
NO idea what to say

```{r}
var <- 'N_elevators'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile
train[,var] %>% cor(train[,target], method='spearman')

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

train[,var] <- train[,var] %>% as.character
boxplot_mano(train, target, var)
train[,var] <- train[,var] %>% as.numeric

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=1)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot() +
  labs(x=var)

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm') +
  labs(x=var, y=target)
```

### SubwayStation
```{r}
var <- 'SubwayStation'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
cor_qual(train, target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])
```



### N_FacilitiesNearBy.PublicOffice.
```{r}
var <- 'N_FacilitiesNearBy.PublicOffice.'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile
train[,var] %>% cor(train[,target], method='spearman')
train %>% cor_qual(target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=1)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot() +
  labs(x=var)

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm') +
  labs(x=var, y=target)
```


### N_FacilitiesNearBy.Hospital.
```{r}
var <- 'N_FacilitiesNearBy.Hospital.'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile
train[,var] %>% cor(train[,target], method='spearman')
train %>% cor_qual(target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=1)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot() +
  labs(x=var)

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm') +
  labs(x=var, y=target)
```
```{r}
train_1 <- train %>% 
  filter(train[,var]==1)

train_2 <- train %>% 
  filter(train[,var]==2)

t.test(train_1[,target], train_2[,target], var.equal=F)
```


### N_FacilitiesNearBy.Dpartmentstore.
```{r}
var <- 'N_FacilitiesNearBy.Dpartmentstore.'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile
train[,var] %>% cor(train[,target], method='spearman')
train %>% cor_qual(target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=1)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot() +
  labs(x=var)

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm') +
  labs(x=var, y=target)
```


### N_FacilitiesNearBy.Mall.
```{r}
var <- 'N_FacilitiesNearBy.Mall.'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile
train[,var] %>% cor(train[,target], method='spearman')
train %>% cor_qual(target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=1)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot() +
  labs(x=var)

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm') +
  labs(x=var, y=target)
```

### N_FacilitiesNearBy.ETC.
```{r}
var <- 'N_FacilitiesNearBy.ETC.'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile
train[,var] %>% cor(train[,target], method='spearman')
train %>% cor_qual(target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=1)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot() +
  labs(x=var)

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm') +
  labs(x=var, y=target)
```
0 vs others

### N_FacilitiesNearBy.Park.
```{r}
var <- 'N_FacilitiesNearBy.Park.'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile
train[,var] %>% cor(train[,target], method='spearman')
train %>% cor_qual(target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=1)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot() +
  labs(x=var)

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm') +
  labs(x=var, y=target)
```

### N_SchoolNearBy.Elementary.
```{r}
var <- 'N_SchoolNearBy.Elementary.'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile
train[,var] %>% cor(train[,target], method='spearman')
train %>% cor_qual(target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=1)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot() +
  labs(x=var)

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm') +
  labs(x=var, y=target)
```


### N_SchoolNearBy.Middle.
```{r}
var <- 'N_SchoolNearBy.Middle.'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile
train[,var] %>% cor(train[,target], method='spearman')
train %>% cor_qual(target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=1)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot() +
  labs(x=var)

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm') +
  labs(x=var, y=target)
```

### N_SchoolNearBy.High.
```{r}
var <- 'N_SchoolNearBy.High.'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile
train[,var] %>% cor(train[,target], method='spearman')
train %>% cor_qual(target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=1)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot() +
  labs(x=var)

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm') +
  labs(x=var, y=target)
```

### N_SchoolNearBy.University.
```{r}
var <- 'N_SchoolNearBy.University.'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile
train[,var] %>% cor(train[,target], method='spearman')
train %>% cor_qual(target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=1)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot() +
  labs(x=var)

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm') +
  labs(x=var, y=target)
```

### N_FacilitiesInApt
```{r}
var <- 'N_FacilitiesInApt'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile
train[,var] %>% cor(train[,target], method='spearman')
train %>% cor_qual(target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=1)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot() +
  labs(x=var)

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm') +
  labs(x=var, y=target)
```

### N_FacilitiesNearBy.Total.
```{r}
corr_pos_Facilities <- c('N_FacilitiesNearBy.Dpartmentstore.',
                         'N_FacilitiesNearBy.Mall.',
                         'N_FacilitiesNearBy.Park.'
                         )
corr_neg_Facilities <- c('N_FacilitiesNearBy.PublicOffice.',
                         'N_FacilitiesNearBy.Hospital.',
                         'N_FacilitiesNearBy.ETC.'
                         )

# N_FacilitiesInApt not counted

train <- train %>% mutate(N_FacilitiesNearby.corr_pos = 
                            N_FacilitiesNearBy.Dpartmentstore. + 
                            N_FacilitiesNearBy.Mall.+
                            N_FacilitiesNearBy.Park.
                         )  

train <- train %>% mutate(N_FacilitiesNearby.corr_neg = 
                            N_FacilitiesNearBy.PublicOffice. + 
                            N_FacilitiesNearBy.Hospital.+
                            N_FacilitiesNearBy.Park.
                         )  
```

```{r}
var <- 'N_FacilitiesNearBy.Total.'
# var <- 'N_FacilitiesNearby.corr_neg'
# var <- 'N_FacilitiesNearby.corr_pos'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile
train[,var] %>% cor(train[,target], method='spearman')
train %>% cor_qual(target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=1)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot() +
  labs(x=var)

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm') +
  labs(x=var, y=target)
```
```{r}
correlation_matrix = train %>% 
  dplyr::select(starts_with('N_Fac'))

correlation_matrix <- cor(cbind(train$SalePrice, correlation_matrix), method='spearman')

corrplot(correlation_matrix, 
         order="hclust", 
         tl.cex = 0.4, 
         type='upper'
         )
```

### N_SchoolNearBy.Total.
```{r}
var <- 'N_SchoolNearBy.Total.'

train[,var] %>% str
train[,var] %>% summary
train[,var] %>% unique
train[,var] %>% quantile
train[,var] %>% cor(train[,target], method='spearman')
train %>% cor_qual(target, var)

ggplot(train, aes(train[,var])) +
  geom_bar() +
  labs(x=var)

boxplot(train[,target]~train[,var], train,
        xlab=var,
        ylab=target)

boxplot_mano(train, target, var)

ridgeline(train[,target], train[,var])


# if numeric
hist_and_density(train, var, binwidth=1)

ggplot(train, aes(x=train[,var], fill=train[,var])) +
  geom_boxplot() +
  labs(x=var)

ggplot(train, aes(x=train[,var], y=train[,target])) +
  geom_point() +
  geom_smooth(method='lm') +
  labs(x=var, y=target)
```
```{r}
correlation_matrix = train %>% 
  dplyr::select(starts_with('N_School'))

correlation_matrix <- cor(cbind(train$SalePrice, correlation_matrix), method='spearman')

corrplot(correlation_matrix, 
         order="hclust", 
         tl.cex = 0.4, 
         type='upper'
         )
```
Zook all N_school and only keep total ?


# EDA by type

```{r}
list(
  'SalePrice',
  'Size.sqf.',
  'YearBuilt',
  'YrSold',
  'MonthSold',
  'N_FacilitiesNearBy.PublicOffice.',
  'N_FacilitiesNearBy.Hospital.',
  'N_FacilitiesNearBy.Dpartmentstore.',
  'N_FacilitiesNearBy.Mall.',
  'N_FacilitiesNearBy.ETC.',
  'N_FacilitiesNearBy.Park.',
  'N_SchoolNearBy.Elementary.',
  'N_SchoolNearBy.Middle.',
  'N_SchoolNearBy.High.',
  'N_SchoolNearBy.University.',
  'N_FacilitiesInApt',
  'N_FacilitiesNearBy.Total.',
  'N_SchoolNearBy.Total.',
  'N_Parkinglot.Ground.',
  'N_Parkinglot.Basement.',
  'N_APT',
  'N_manager',
  'N_elevators',
  'Floor'
) -> quantitative_vars

list(
  'HallwayType',
  'HeatingType',
  'AptManageType',
  'TimeToBusStop',
  'TimeToSubway',
  'SubwayStation'
) -> qualitative_vars

length(quantitative_vars) + length(qualitative_vars) == length(train)

for (var in quantitative_vars)
    train[,var] <- train[,var] %>% as.numeric()


qualitative_vars <- unlist(qualitative_vars)
quantitative_vars <- unlist(quantitative_vars)
```

## EDA for quantitative variables
```{r}
train_quant <- train[, quantitative_vars]
train_quant %>% colnames()
```
###


```{r}
for(var in train_quant){
  hist(var)
}
```
```{r}
ggplot(train_quant) +
  geom_histogram(aes(SalePrice), binwidth=10000) +
  geom_density(aes(SalePrice)) 
```


```{r}
for (var_name in colnames(train_quant)){
    print(
      ggplot(train_quant, aes(get(var_name))) +
        geom_density() +
        ggtitle(var_name)*
        # geom_line(aes(Date, get(elem))) +
        # geom_point(aes(Date, get(elem)))

        # theme_minimal() +
        # xlab("Date") +
        # ylab("Values") +
        # scale_color_manual(values = c("elem"="#B22222"), labels= c(elem)) +
        # labs(colors = "legends")
    )
}
```


## EDA for qualitative variables
```{r}
train_qual <- train[, qualitative_vars]
```

```{r}

```




